Novel improvements in the Material Point Method to face dynamic problems: Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This study was funded by Agustín de Betancourt Foundation (grant number 262390106114).}

### 2020-03-11 Figures/Block.tex
Cambios 11-3-2020

%%%%%%%%%%%%%%%%
\beam{2}{12}{7};
\beam{2}{7}{6};
\beam{2}{6}{11};
\beam{2}{12}{11};

@@

%%%%%%%%%%%%%%%%
\beam{2}{7}{4};
\beam{2}{4}{3};
\beam{2}{3}{6};
\beam{2}{7}{6};

@@

% Gravity
\point{g}{12}{5};
\load{1}{g}[90][3][0];

% Cotas
\dimensioning{1}{23}{36}{-1.5}[$10~m$];
\dimensioning{2}{23}{1}{-1.5}[$10~m$];

>>>>

% %%%%%%%%%%%%%%%%
\beam{2}{12}{7};
\beam{2}{7}{6};
\beam{2}{6}{11};
\beam{2}{12}{11};

@@

% %%%%%%%%%%%%%%%%
\beam{2}{7}{4};
\beam{2}{4}{3};
\beam{2}{3}{6};
\beam{2}{7}{6};

@@

% Gravity
\draw[->, line width=1mm] (12,6)--(12,4);
\node[color=black, very thick] at (17,5)
{\LARGE$\mathbf{g}(t)= \left\{
    \begin{array}{ll}
      0.5 \mathbf{g} (\sin(\frac{2t \pi}{T} - \frac{\pi}{2})+1)  & \mbox{if } t \leq T/2 \\
      \mathbf{g} & \mbox{if } t > T/2
    \end{array}
  \right.$};

% Cotas
\dimensioning{1}{23}{36}{-2}[\LARGE$10~m$];
\dimensioning{2}{23}{1}{-2}[\LARGE$10~m$];

% GPS
\draw plot [only marks, mark=square*] coordinates {(0.422650, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 1.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 0.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 3.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 2.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 5.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 4.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 7.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 6.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(0.422650, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(1.577350, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(2.422650, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(3.577350, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(4.422650, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(5.577350, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(6.422650, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(7.577350, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 9.577350)}; 
\draw plot [only marks, mark=square*] coordinates {(8.422650, 8.422650)}; 
\draw plot [only marks, mark=square*] coordinates {(9.577350, 8.422650)};
